Do investors in clean energy ETFs herd?

### 2025-03-21 alt_energy_herding.qmd
vassilias comments

@@

Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2016 and 2024. We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets. Methodologically, we follow the standard herding tests by @christie1995 and @chang2000. The traditional approach was supplemented by quantile regressions [@koenker1978 ] in order to capture the time-varying aspects of herding. Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour. The next section describes the data and methodology, followed by the results and conclusions.

@@

@@

where $R_{i,t}$ is the return and $R_{m,t}$ is the cross sectional average of returns for the sample of ETFs available for each day. The return dispersion measures the directional similarity of ETF returns to the market return. This return similarity forms the basis for the herding behaviour tests. The CSAD measure for US Alternative Energy ETFs is presented in @fig-csad. Following @galariotis2015 we estimate @eq-herding:

@@

## Herding behaviour over-time

There is ample evidence that herding might be time dependent [see @babalos2015; @klein2013; @stavroyiannis2019]. In order to gain further insight on the time varying nature of herding we conducted a rolling window analysis. The size of the rolling window is related to the time-scales of the system (response times), and the aim of the research [@babalos2015]. There is no golden rule for the right size of the rolling window, there is a trade-off between having a long enough window to estimate the metrics, and short enough to have a sufficient number of windows in order to be able to derive a trend. In light of the above discussion we set off to conduct a rolling window analysis of 50 observations. @fig-rolling_window plots the time evolution of the value of the estimated significance of the herding coefficient ($\gamma_2$) using the rolling window analysis.

@@

The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies. There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets. @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.  It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets. Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.

@@

The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.^[It should be noted that due to availability issues the probit analysis ends in December of 2023.] In other words, climate risks is good news for clean energy stocks or firms resulting in anti-herding behaviour. This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products. As a result, the cross sectional dispersion of clean energy ETFs tends to increase.

@@

## Cross-sectional average deviations

@@

tribble(
  ~"ETF",
  "ALPS CLEAN ENERGY ETF",
  "BLUE HORIZON BNE ETF",
  "SPDR S&P KENSHO CLEAN POWER ETF",
  "GLOBAL X CLEANTECH ETF",
  "PROSHARES S&P KENSHO CLEANTECH ETF",
  "INVESCO MSCI SUSTAINABLE FUTURE ETF",
  "FIRST TRUST GLOBAL WIND ENERGY ETF",
  "FIDELITY CLEAN ENERGY ETF",
  "GLDS.BLOOMBERG CN. EN. EQ.ETF",
  "FST.NQ.CN.EDGE SMRT.GRID INFRA IDX ETF",
  "DEFIANCE NEXT GEN H2 ETF",
  "DIREXION HYDROGEN ETF",
  "GLOBAL X HYDROGEN ETF",
  "ISHARES GLOBAL CLEAN EN. ETF",
  "BLACKR.WLD.EXUS CRBN TSTN.READINESS",
  "NUB.CBN.TSTN.& INFRA",
  "TCW TRANSFORM SYSTEMS ETF",
  "VANECK URANIUM AND NUCLEAR ENERGY",
  "NUVEEN GLOBAL NET ZERO TRANSITION ETF",
  "SPDR MSCI USA CIM. PA. ALIGNED ETF", 
  "INVESCO GLOBAL CLEAN ENERGY ETF", 
  "FST.NQ.CN.EDGE GREY.ETF",
  "GLOBAL X SOLAR ETF", 
  "GLOBAL X RENEWABLE ENERGY PRODUCERS",
  "TRUESHARES EAG.GLB. RENWEN.ETF",
  "VANECK LOW CARBON ENERGY ETF",
  "SMARTETFS SUST.EN. II ETF",
  "INVESCO SOLAR ETF", 
  "VIRTUS DUFF & PHELPS CLEAN ENERGY ETF",
  "GLOBAL X WIND ENERGY ETF"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1,  part = "all") %>%
  add_footer_row(values = as_paragraph("Note: Details on this funds can be found on Yahoo Finance."), colwidths = 1) %>% 
  autofit(add_w = 3)

>>>>

It is well established that herding literature is vast with contradictory results depending mainly on the market, the employed methodology and the period under consideration [@spyrou2013]. Herding behavior can be either spurious in cases when investors make similar decisions as a result of processing the same information set and intentional herding when investors imitate the actions of others [see inter alia, @bikhchandani2000; @galariotis2015]. Empirical studies on herding usually fall into two categories: namely those that employ holdings data aiming at measuring institutional investor herding [@lakonishok1992], and studies that use market returns data and investigate herding towards the market consensus [@chang2000; @galariotis2015]. Our paper falls within the latter category and tests for herding towards the market consensus for clean energy US ETFs.

@@

Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2016 and 2024. We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets. Methodologically, we follow the standard herding tests by @christie1995 and @chang2000. The traditional approach was supplemented by quantile regressions [@koenker1978 ] in order to capture the time-varying aspects of herding. Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour.

The next section describes the data and methodology, followed by the results and conclusions.

@@

The development of the CSAD measure over time for the clean energy ETFs is presented in @fig-csad. In general, the CSAD measure remains within certain bounds. However, we observe several cases when the CSAD measure deviates significantly from the market consensus: around the announcement of the Paris agreement (2016-2017), the covid-19 pandemic crisis (2020–2021), the war outbreak in Ukraine (2022) among others. @tbl-desc presents the descriptive statistics of the data.

```{r}
#| label: tbl-desc
#| tbl-cap: "Descriptive statistics of the data"
#| cache: false

tribble(
  ~ " ", ~ "Mean", ~ "St.dev", ~ "Skewness", ~ "Kurtosis",
  "CSAD",  "0.0062", "0.0034", "1.5598", "7.9355",
  "Absolute CSAD",  "0.0094", "0.0107", "3.3175", "23.8725"
) |> 
  flextable_pdf() |> 
  align(align = "left", j = 1, part = "all") |>
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) |> 
  autofit(add_w = 0.6)

@@

where $R_{i,t}$ is the return and $R_{m,t}$ is the cross sectional average of returns for the sample of ETFs available for each day. The return dispersion measures the directional similarity of ETF returns to the market return. This return similarity forms the basis for the herding behaviour tests. Following @galariotis2015 we estimate @eq-herding:

@@

## Time-varying herding behaviour

There is ample evidence that herding might vary in response to market conditions [see @babalos2015; @klein2013; @stavroyiannis2019]. In order to gain further insight on the time varying nature of herding we conducted a rolling window analysis. The size of the rolling window is related to the time-scales of the system (response times), and the aim of the research [@babalos2015]. There is no golden rule for the right size of the rolling window, there is a trade-off between having a long enough window to estimate the metrics, and short enough to have a sufficient number of windows in order to be able to derive a trend. In light of the above discussion we set off to conduct a rolling window analysis of 50 observations. @fig-rolling_window plots the time evolution of the value of the estimated significance of the herding coefficient ($\gamma_2$) using the rolling window analysis.

@@

The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies. In particular, following the implementation of the Paris agreement in November 2016, climate policy uncertainty has become in the epicenter of interest across carbon and energy markets. There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets [see inter alia, @gabriel2024; @bolton2021; @krueger2020]. To this end, @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.  It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets. Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.

@@

The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.^[It should be noted that due to availability issues the probit analysis ends in December of 2023.] In other words, climate risks is good news for clean energy stocks or firms resulting in anti-herding behaviour. This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products. As a result, the cross-sectional dispersion of clean energy ETFs tends to increase. Our results are in line with those of rrelevant studies such as Gabriel & Pinho (2024) who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.

@@

@@

tribble(
  ~"ETF",
  "ALPS CLEAN ENERGY ETF",
  "BLUE HORIZON BNE ETF",
  "SPDR S&P KENSHO CLEAN POWER ETF",
  "GLOBAL X CLEANTECH ETF",
  "PROSHARES S&P KENSHO CLEANTECH ETF",
  "INVESCO MSCI SUSTAINABLE FUTURE ETF",
  "FIRST TRUST GLOBAL WIND ENERGY ETF",
  "FIDELITY CLEAN ENERGY ETF",
  "GLDS.BLOOMBERG CN. EN. EQ.ETF",
  "FST.NQ.CN.EDGE SMRT.GRID INFRA IDX ETF",
  "DEFIANCE NEXT GEN H2 ETF",
  "DIREXION HYDROGEN ETF",
  "GLOBAL X HYDROGEN ETF",
  "ISHARES GLOBAL CLEAN EN. ETF",
  "BLACKR.WLD.EXUS CRBN TSTN.READINESS",
  "NUB.CBN.TSTN.& INFRA",
  "TCW TRANSFORM SYSTEMS ETF",
  "VANECK URANIUM AND NUCLEAR ENERGY",
  "NUVEEN GLOBAL NET ZERO TRANSITION ETF",
  "SPDR MSCI USA CIM. PA. ALIGNED ETF", 
  "INVESCO GLOBAL CLEAN ENERGY ETF", 
  "FST.NQ.CN.EDGE GREY.ETF",
  "GLOBAL X SOLAR ETF", 
  "GLOBAL X RENEWABLE ENERGY PRODUCERS",
  "TRUESHARES EAG.GLB. RENWEN.ETF",
  "VANECK LOW CARBON ENERGY ETF",
  "SMARTETFS SUST.EN. II ETF",
  "INVESCO SOLAR ETF", 
  "VIRTUS DUFF & PHELPS CLEAN ENERGY ETF",
  "GLOBAL X WIND ENERGY ETF"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1,  part = "all") %>%
  add_footer_row(values = as_paragraph("Note: Details on these funds can be found on Yahoo Finance."), colwidths = 1) %>% 
  autofit(add_w = 3)

### 2025-03-21 alt_energy_herding.tex
vassilias comments

@@

Therefore, this study investigates herding behaviour in alternative
energy ETFs in the US between 2016 and 2024. We then demonstrate how
climate-related uncertainty can drive herding behaviour in these
markets. Methodologically, we follow the standard herding tests by
\citet{christie1995} and \citet{chang2000}. The traditional approach was
supplemented by quantile regressions \citep{koenker1978} in order to
capture the time-varying aspects of herding. Lastly, we extend recent
approaches by \citet{bua2024} and others, which seek to establish a link
between climate uncertainty and herding behaviour. The next section
describes the data and methodology, followed by the results and
conclusions.

@@

@@

where \(R_{i,t}\) is the return and \(R_{m,t}\) is the cross sectional
average of returns for the sample of ETFs available for each day. The
return dispersion measures the directional similarity of ETF returns to
the market return. This return similarity forms the basis for the
herding behaviour tests. The CSAD measure for US Alternative Energy ETFs
is presented in Figure~\ref{fig-csad}. Following \citet{galariotis2015}
we estimate Equation~\ref{eq-herding}:

@@

\subsection{Herding behaviour
over-time}\label{herding-behaviour-over-time}

There is ample evidence that herding might be time dependent
\citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In order to
gain further insight on the time varying nature of herding we conducted
a rolling window analysis. The size of the rolling window is related to
the time-scales of the system (response times), and the aim of the
research \citep{babalos2015}. There is no golden rule for the right size
of the rolling window, there is a trade-off between having a long enough
window to estimate the metrics, and short enough to have a sufficient
number of windows in order to be able to derive a trend. In light of the
above discussion we set off to conduct a rolling window analysis of 50
observations. Figure~\ref{fig-rolling_window} plots the time evolution
of the value of the estimated significance of the herding coefficient
(\(\gamma_2\)) using the rolling window analysis.

@@

The behaviour of participants in energy markets is closely related to
the developments in the field of climate risks, carbon emissions and
environmentally friendly policies. There are a few studies that attempt
to quantify the effects of uncertainty related to climate on the economy
and financial markets. \citet{bua2024} developed two climate risk
related indexes namely transition and physical risk using a text-based
approach in order to study the effect of these risks in financial
markets. It is expected that investors would prefer to hold assets that
perform well in the face of increasing climate change risks, even if
this entails accepting lower returns for such climate-hedging assets.
Therefore, in the context of our study and following previous studies
that study the determinants of herding behaviour
\citep[see][]{bouri2019, demirer2018}, we attempt to study the effect of
climate-related uncertainty on the formation of herding behavior in the
clean energy market.

@@

The results from the Probit model are reported in
Table~\ref{tbl-probit_analysis}, where only the physical risk index
significantly decreases the probability of herding.\footnote{It should
  be noted that due to availability issues the probit analysis ends in
  December of 2023.} In other words, climate risks is good news for
clean energy stocks or firms resulting in anti-herding behaviour. This
implies that in the presence of higher physical risk with respect to the
climate, clean energy ETFs become a more attractive investment option
for investors that allocate their money to the various alternative
energy investment products. As a result, the cross sectional dispersion
of clean energy ETFs tends to increase.

@@

\subsection{Cross-sectional average
deviations}\label{cross-sectional-average-deviations}

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ this\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\

>>>>

It is well established that herding literature is vast with
contradictory results depending mainly on the market, the employed
methodology and the period under consideration \citep{spyrou2013}.
Herding behavior can be either spurious in cases when investors make
similar decisions as a result of processing the same information set and
intentional herding when investors imitate the actions of others
\citep[see inter alia,][]{bikhchandani2000, galariotis2015}. Empirical
studies on herding usually fall into two categories: namely those that
employ holdings data aiming at measuring institutional investor herding
\citep{lakonishok1992}, and studies that use market returns data and
investigate herding towards the market consensus
\citep{chang2000, galariotis2015}. Our paper falls within the latter
category and tests for herding towards the market consensus for clean
energy US ETFs.

@@

Therefore, this study investigates herding behaviour in alternative
energy ETFs in the US between 2016 and 2024. We then demonstrate how
climate-related uncertainty can drive herding behaviour in these
markets. Methodologically, we follow the standard herding tests by
\citet{christie1995} and \citet{chang2000}. The traditional approach was
supplemented by quantile regressions \citep{koenker1978} in order to
capture the time-varying aspects of herding. Lastly, we extend recent
approaches by \citet{bua2024} and others, which seek to establish a link
between climate uncertainty and herding behaviour.

The next section describes the data and methodology, followed by the
results and conclusions.

@@

The development of the CSAD measure over time for the clean energy ETFs
is presented in Figure~\ref{fig-csad}. In general, the CSAD measure
remains within certain bounds. However, we observe several cases when
the CSAD measure deviates significantly from the market consensus:
around the announcement of the Paris agreement (2016-2017), the covid-19
pandemic crisis (2020--2021), the war outbreak in Ukraine (2022) among
others. Table~\ref{tbl-desc} presents the descriptive statistics of the
data.

\begin{longtable}[l]{|p{1.46in}|p{1.08in}|p{1.08in}|p{1.23in}|p{1.14in}}

\caption{\label{tbl-desc}Descriptive statistics of the data}

\ascline{1pt}{000000}{1-5}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Mean}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{St.dev}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Skewness}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Kurtosis}}}} \\

\ascline{1pt}{000000}{1-5}\endfirsthead

\ascline{1pt}{000000}{1-5}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Mean}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{St.dev}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Skewness}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Kurtosis}}}} \\

\ascline{1pt}{000000}{1-5}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0062}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0034}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1.5598}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{7.9355}}}} \\

\ascline{1pt}{FFFFFF}{1-5}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\

\ascline{1pt}{000000}{1-5}

@@

where \(R_{i,t}\) is the return and \(R_{m,t}\) is the cross sectional
average of returns for the sample of ETFs available for each day. The
return dispersion measures the directional similarity of ETF returns to
the market return. This return similarity forms the basis for the
herding behaviour tests. Following \citet{galariotis2015} we estimate
Equation~\ref{eq-herding}:

@@

\subsection{Time-varying herding
behaviour}\label{time-varying-herding-behaviour}

There is ample evidence that herding might vary in response to market
conditions \citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In
order to gain further insight on the time varying nature of herding we
conducted a rolling window analysis. The size of the rolling window is
related to the time-scales of the system (response times), and the aim
of the research \citep{babalos2015}. There is no golden rule for the
right size of the rolling window, there is a trade-off between having a
long enough window to estimate the metrics, and short enough to have a
sufficient number of windows in order to be able to derive a trend. In
light of the above discussion we set off to conduct a rolling window
analysis of 50 observations. Figure~\ref{fig-rolling_window} plots the
time evolution of the value of the estimated significance of the herding
coefficient (\(\gamma_2\)) using the rolling window analysis.

@@

The behaviour of participants in energy markets is closely related to
the developments in the field of climate risks, carbon emissions and
environmentally friendly policies. In particular, following the
implementation of the Paris agreement in November 2016, climate policy
uncertainty has become in the epicenter of interest across carbon and
energy markets. There are a few studies that attempt to quantify the
effects of uncertainty related to climate on the economy and financial
markets \citep[see inter alia,][]{gabriel2024, bolton2021, krueger2020}.
To this end, \citet{bua2024} developed two climate risk related indexes
namely transition and physical risk using a text-based approach in order
to study the effect of these risks in financial markets. It is expected
that investors would prefer to hold assets that perform well in the face
of increasing climate change risks, even if this entails accepting lower
returns for such climate-hedging assets. Therefore, in the context of
our study and following previous studies that study the determinants of
herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
study the effect of climate-related uncertainty on the formation of
herding behavior in the clean energy market.

@@

The results from the Probit model are reported in
Table~\ref{tbl-probit_analysis}, where only the physical risk index
significantly decreases the probability of herding.\footnote{It should
  be noted that due to availability issues the probit analysis ends in
  December of 2023.} In other words, climate risks is good news for
clean energy stocks or firms resulting in anti-herding behaviour. This
implies that in the presence of higher physical risk with respect to the
climate, clean energy ETFs become a more attractive investment option
for investors that allocate their money to the various alternative
energy investment products. As a result, the cross-sectional dispersion
of clean energy ETFs tends to increase. Our results are in line with
those of rrelevant studies such as Gabriel \& Pinho (2024) who claimed
that in the event of climate policy shocks, clean energy assets could
serve the role of hedging instruments.

@@

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ these\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\
